Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 17

tsne_plot_mnist_clust <- ggplot() + 
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c('#d9d9d9', '#ff7f00')) +
  interior_annotation("a", c(0.08, 0.93), cex = 2) +
  theme(legend.position = "none")

@@

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    title = "b", 
    cex = 2, 
    axis_text_size = 3, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

@@

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    title = "c", 
    cex = 2, 
    axis_text_size = 3, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

>>>>

tsne_plot_mnist_clust <- ggplot() + 
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c('#d9d9d9', '#ff7f00')) +
  interior_annotation("a", c(0.08, 0.93), cex = 2.5) +
  theme(legend.position = "none")

@@

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    title = "b", 
    cex = 2.5, 
    axis_text_size = 3, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

@@

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    title = "c", 
    cex = 2.5, 
    axis_text_size = 3, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )
